Procedural generation of levels for the angry birds videogame using evolutionary computation\\

### 2019-05-15 IEEE_ConferenceOnGames/new_article.tex
Modification to conclusions

>>>>

    We were able to fulfill our objective of generating levels that could be played, 
    however as seen in our figures the current state of this system is still in development 
    phase, and some modifications must be applied in order to optimize some aspects of it, 
    by using a different way of generating individual we were able to reduce the process 
    time requierd on a full system execution however we require to search for a way to 
    avoid using the software to evaluate the individuals, this way we expect to reduce 
    drastically the time required to process the data of the levels.
